\documentclass{article}

\usepackage[fontsize=9.8pt]{fontsize}

% We use 0.5in margins for the resume.
\usepackage[margin=0.5in]{cv}

% Disable page numbers.
\pagenumbering{gobble}

% Adjust column widths.
\setlength{\cvleftcolumnwidth}{1in}
\setlength{\cvrightcolumnwidth}{6.25in}

% Set header information.
\name{Pierce}{Darragh}
\location{University of Maryland, MD, USA}
\email{pierce.darragh@gmail.com}
\website{pdarragh.github.io}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Biographical Information
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\makeheader{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Education
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Education}

\begin{cvlist}
  % UMD
  \cvsubheading{University of Maryland}{College Park, MD, USA}
  \cvdegree[\ ]{2021--Present}{PhD in Computer Science, advised by Dr. David Van
    Horn}

  % U of U
  \cvgap\cvsubheading{University of Utah}{Salt Lake City, UT, USA}
  \cvdegree[GPA:\ 3.3/4]{2012--2018}{BS/MS in Computer Science, Minor in
    Linguistics}

  \cvinfo{}
\end{cvlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Experience
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Research and Industrial Experience}

\begin{cvlist}
  %% MARYLAND
  \cvsubheading{University of Maryland}{College Park, MD, USA}

  % RA
  \cvposition{2021--Present}{Graduate Research Assistant}{PI: David Van Horn}
  \cvitem{Develop a86 interpreter and debugging environment for CMSC 430.}
  \cvitem{Keep up to date with recent literature.}

  % CMSC 430 TA
  \cvposition{2022--Present}{Graduate Teaching Assistant}{CMSC 430: Compilers}
  \cvitem{Hold office hours, answer online questions, and help write and grade
    quizzes and exams.}
  \cvitem{Implement and revise assignment autograders.}
  \cvitem{Keep notes from student interactions to discuss course pedagogy with
    instructors.}

  %% UTAH
  \cvgap\cvsubheading{University of Utah}{Salt Lake City, UT, USA}

  % SweetPea
  \cvposition{2020--2021}{Research Associate}{PI:\ Matthew Flatt}
  \cvinfo{Contributed to research on SweetPea: a Python DSL for specifying
    factorial experimental designs and automatically generating trial sequences
    according to given constraints using SAT sampling.}
  \cvitem{Translated back-end from Haskell to Python, improving robustness to
    reduce possible errors.}
  \cvitem{Expanded expressive capabilities and improved user interface to
    match.}
  \cvitem{Implemented automated continuous integration with GitHub Actions.}

  % Flux
  \cvposition{2019--2020}{Research Associate}{PI:\ Eric Eide}
  \cvinfo{Contributed to research on Xsmith: a Racket DSL for creating random
    generators of semantically valid programs for any language. Xsmith is a
    spiritual successor to Csmith.}
  \cvitem{Implemented Xsmith's Python language specification.}
  \cvitem{Implemented a dedicated library to improve Xsmith's capabilities for
    exploring state spaces (Clotho).}
  \cvitem{Published and presented \textit{Clotho: A Racket Library for
      Parametric Randomness}.}

  % U Combinator (post-graduation)
  \cvposition{2018--2019}{Research Associate}{PI:\ Michael D. Adams}
  \cvitem{Published and presented \textit{Parsing with Zippers}, a new general
    parsing algorithm.}

  % Apple Internship
  \cvgap\cvsubheading{Apple, Inc.}{Cupertino, CA, USA}
  \cvposition{Summer 2017}{Software Engineer Intern}{Apple Information Security}
  \cvitem{Designed, built, and presented a secure framework for creating proxy
    servers for penetration testing.}

  % U Combinator (in-school)
  \cvgap\cvsubheading{University of Utah}{Salt Lake City, UT, USA}
  \cvposition{2016--2018}{Research Assistant}{PIs:\ Matt Might, Michael D.
    Adams}
  \cvinfo{Contributed to research on JAAM: a whole-program static analyzer
    written in Scala built for identifying potential side-channel
    vulnerabilities in compiled Java applications.}
  \cvitem{Twice selected as one of three student lab members sent to DARPA
    competition for evaluating JAAM.}

  \cvinfo{}
\end{cvlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Publications
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Publications}

\begin{cvlist}
  %% Xsmith
  \cvseparate[GPCE 2023]{\textit{Generating Conforming Programs with
      Xsmith.}}{\cvurl{http://www.flux.utah.edu/paper/hatch-gpce23}}
  %
  \cvinfo{William Gallard Hatch, \underline{Pierce Darragh}, Sorawee
    Porncharoenwase, Guy Watson, Eric Eide.}

  %% SweetPea
  \cvseparate[BehRes 2021]{\textit{SweetPea: A standard language for factorial
      experimental design.}}{\cvurl{pdarragh.github.io/p/sweetpea}}
  %
  \cvinfo{Sebastian Musslick, Anastasia Cherkaev, Ben Draut, Ahsan Sajjad Butt,
    \underline{Pierce Darragh}, Vivek Srikumar, Matthew Flatt, Jonathan D
    Cohen.}

  %% Clotho
  \cvseparate[Scheme 2020]{\textit{Clotho: A Racket Library for Parametric
      Randomness.}}{\cvurl{pdarragh.github.io/p/scheme20}}
  %
  \cvinfo{\underline{Pierce Darragh}, William Gallard Hatch, and Eric Eide.}

  %% PwZ
  \cvseparate[ICFP 2020]{\textit{Parsing with Zippers (Functional
      Pearl).}}{\cvurl{pdarragh.github.io/p/icfp20}}
  %
  \cvinfo{\underline{Pierce Darragh} and Michael D. Adams.}

  \cvinfo{}
\end{cvlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Awards, Leadership, and Service
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Awards, Leadership, and Service}

\begin{cvlist}
  \cvaward{2021--Present}{Recipient of the Dean's Fellowship, sponsored by the
    University of Maryland's CS department.}
  \cvservice{2020--2022}{Community manager for Dr.\ Jean Yang's
    \texttt{\#PLTalk} \cvurl[Twitch stream]{twitch.tv/jeanqasaur} and
    \cvurl[Discord server]{discord.gg/TZvcCKrs4V}.}
  \cvservice{2019--2021}{Organizer of weekly Programming Languages
    Reading Group at the University of Utah.}
  \cvservice{2014--2015}{Men's Team Captain, University of Utah Club Swim Team.}
  \cvservice{2013, 2014}{Volunteer judge for elementary student projects at Salt
    Lake Valley Science and Engineering Fair.}
  \cvaward{2012--2016}{Recipient of the National Merit Scholarship, sponsored by
    E\raisebox{0.2ex}{\textasteriskcentered{}}TRADE.}
  \cvaward{2012--2013}{Recipient of the Merit Scholarship with Presidential
    Honors, sponsored by the University of Utah.}
\end{cvlist}

\end{document}